\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Acknowledge funders

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklags, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor Launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (Secure Computing Research for Users' Benefit)~\cite{scrub}, and BLUES (Berkeley Laboratory for Usable and Experimental Security)~\cite{blues} laboratories, with support from
Intel, the National Science Foundation,
the Open Technology Fund through the Freedom2Connect Foundation, and from
the US Department of State, Bureau of Democracy, Human Rights and Labor.

>>>>

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklags, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor Launcher and internal constraints. We gratefully acknowledge assistance from the Xlab (Experimental Social Science Laboratory)~\cite{xlab} and
financial support from Intel through the ISTC for Secure Computing,
the National Science Foundation through award CNS-1318680,
the Open Technology Fund through the Freedom2Connect Foundation,
the US Department of State, Bureau of Democracy, Human Rights and Labor,
the AFOSR under MURI award FA9550-12-1-0040,
and the Hewlett Foundation through the Center for Long-Term Cybersecurity.
